### 2019-04-29 thesis_proposal_LaTeX/Chapters/3_HypothesisAndResearchQuestions.tex
2nd draft Done
proposal update

\subsubsection*{\color{mygray}[Chapter ready for review]}
% The system/technique/parameter X is better, for task Y, than each of its rivals Z, in dimension W.

@@

The rheological properties of polymer solutions along with synthesis parameters (stage velocity, voltage, dispense rate) can be amended through rheological analyses to obtain a low voltage electrospun-able, photopolymerizable and graphitizable fibers for the synthesis of carbon nano-wires with specified dimensions (diameter and length).

@@

\begin{itemize}
	\item{
	Is there any evidence of carbon nano-wire fabrication though electrospun-able and pyrozable polymer solutions?
	}
	\item{
	What are the process parameters to consider/control for the fabrication processes of carbon nano-wires? 
	}
	\item{
	What rheological properties are to be controlled/tested to deliver a electrospun-able and pyrozable polymer solution?	
	}
	\item{
	Are there any efforts employed to the design of polymer solutions that can be electrospun, photopolymerized, and pyrolyzed into conducting carbon nanowires?
	}
	\item{
	Are the optimal fabrication parameters defined \cite{Cardenas2017} for the synthesis of carbon nano-wires through near-field electromechanical spinning?	
	}
\end{itemize}

>>>>

%\subsubsection*{\color{mygray}[Chapter ready for review]}
% The system/technique/parameter X is better, for task Y, than each of its rivals Z, in dimension W.

@@

The rheological properties of polymer solutions along with synthesis parameters (stage velocity, voltage, dispense rate) can be amended through rheological analyses to obtain a low voltage electrospun-able, photopolymerizable and graphitizable fibers for the synthesis of carbon nano-wires with specified dimensions (diameter and length). The rheological properties of polymer solutions along with synthesis parameters are to be amended by replacing the PEO (Poly(ethylene) oxide) component within the existing polymer solutions described in Flores \cite{Flores2017} and Cardemas \cite{Cardenas2017} work. PEO is to be replaced as its only purpose is to allow the electrospinning process to take place, but not benefit is obtained from it after pyrolysis.

@@

\begin{itemize}
	\item{
	Is there any evidence of carbon nano-wire fabrication though electrospun-able and pyrozable polymer solutions?
	}
	\item{
	What are the process parameters to consider/control for the fabrication processes of carbon nano-wires? 
	}
	\item{
	What rheological properties are to be controlled/tested to deliver a electrospun-able and pyrozable polymer solution?	
	}
	\item{
	Are there any efforts employed to the design of polymer solutions that can be electrospun, photopolymerized, and pyrolyzed into conducting carbon nanowires?
	}
	\item{
	Are the optimal fabrication parameters defined \cite{Cardenas2017} for the synthesis of carbon nano-wires through near-field electromechanical spinning?	
	}
	\item{
	What PEO-similar materials can be used to allow the electrospinning technique and favor the carbon nano-wire properties after pyrolysis? 
	}
\end{itemize}

### 2019-04-29 thesis_proposal_LaTeX/Chapters/5_TheoreticalFramework.tex
proposal update

>>>>

\section{Polymer Solutions}
Polymer solutions display viscoelastic properties that provide unique properties due to their macromolecules. their chains are long and entangled. When a shear force is applied, the solution creates a large interaction between the molecules, hence the viscosity depends not only on temperature and shear, but also molecular weight distribution and concentration. The solvent also affects the viscosity \cite{Flores2017, Huang2003, Baumgarten1971}.

\begin{figure}[th]
\centering
\includegraphics[width=0.50\textwidth]{./Figures/goodbadsolvent.png}
\decoRule
\caption[Effects in polymer chains dimensions due to solvent quality]{Effects in polymer chains dimensions due to solvent quality \cite{Flores2017}}
\label{fig:goodbadsolvent}
\end{figure}

Figure \ref{fig:goodbadsolvent} shows how the quality of a solvent affects the polymer distribution within the solution. Moreover the prsence of electrolites also modify the structure of the polymer threads. In non-ionic solvents, the charges are distributed along the chains and their own repulsion stretches the polimer threads into a more aligned configuration when an electrolyte is added, as detailed in Figure \ref{fig:electrolyteConcentration}.

\begin{figure}[th]
\centering
\includegraphics[width=0.50\textwidth]{./Figures/electrolyteConcentration.png}
\decoRule
\caption[Effects of electrolyte in polymer chain dimensions]{Effects of electrolyte in polymer chain dimensions \cite{Flores2017}}
\label{fig:electrolyteConcentration}
\end{figure}

\section{Rheometry}
Rheometry is the measuring technology used to determine rheological data. There are different measuring systems, instruments and analysis methods. Both, liquids and solid  can be investigated using rotational and oscillatory rheometers. Rotational tests are performed to characterize viscous behavior. In order to evaluate viscoelastic behavior, creep tests, relaxation tests and oscillatory tests are performed \cite{Flores2017}.

\subsection{Amplitude Sweep}
An amplitude sweep is a typical test used to characterize the behavior of a polymer
solution or polymer melt. In this basic test a constant angular frequency is applied along with an increasing or decreasing deformation or strain, see Figure \ref{fig:ampSweep} a). The obtained results are the storage and loss moduli, $G'$ and $G''$ respectively, along the values of percentage of strain applied. The amplitude is the maximum of the oscillatory motion. Normally at low frequencies the viscoelastic material presents a linear behavior, this is when the viscoelastic properties are independent of the strain or stress imposed due to the structure of the material stays undisturbed. Nevertheless, as the amplitude is increased at some at some point this linear trend changes suddenly. Once this critical amplitude value is reached the material becomes more elastic or viscous depending on the solution initial state, see Figure \ref{fig:ampSweep} b) \cite{Flores2017}.

\begin{figure}[th]
\centering
\includegraphics[width=0.75\textwidth]{./Figures/ampSweep.png}
\decoRule
\caption[Amplitude Sweep]{a) Imposed amplitude along time with constant frequency. b) Results for an amplitude sweep \cite{Flores2017}}
\label{fig:ampSweep}
\end{figure}

\subsection{Frequency Sweep}
A frequency sweep, is a common oscillatory test useful to understand the rheological behavior of fluids as it measures the viscoelastic properties. This measurement is considered a viscoelastic spectrum, in general, the shorter the timescale the more elastic the material behaves. These results are related to the molecular structure of the sample. Figure \ref{fig:freqSweep} shows a typical data for a polymer melt where different regions are observed. Frequency sweep measurements also allow the estimation of the molecular weight distribution characteristics such as entanglement density and process-ability \cite{Flores2017}.

\begin{figure}[th]
\centering
\includegraphics[width=0.75\textwidth]{./Figures/freqSweep.png}
\decoRule
\caption[Frequency Sweep]{Typical results for a frequency sweep. \cite{Flores2017}}
\label{fig:freqSweep}
\end{figure}

\subsection{Flow Curve}
The viscosity is measured as a function of the shear rate in a rotational rheometer with different geometries according to the sample. Normally three types of behaviours can be characterized in flow curve measurements: a) ideal viscous, b) shear thinning and c) shear thickening. Figure \ref{fig:flowCurve} shows three different materials and their response to an imposed shear rate \cite{Flores2017}.

\begin{figure}[th]
\centering
\includegraphics[width=0.75\textwidth]{./Figures/flowCurve.png}
\decoRule
\caption[Flow Curves]{a) Flow curve stress vs stress. b) Flow curve strain vs shear viscosity. Both figures for i Newtonian fluid, ii Shear thinning fluid, iii Shear thickening fluid. \cite{Flores2017}}
\label{fig:flowCurve}
\end{figure}

### 2019-04-29 thesis_proposal_LaTeX/Chapters/6_StateoftheArt.tex
more state of the art
proposal update

\subsection{Rheological Characterization : \textbf{Flow Curve}}

Figure \ref{fig:SerieAflowCurve} shows evidence that the equal increase of PEO and TBATFB concentrations result in an increase of shear viscosity rate $\gamma$. for concentrations from 1.00 to 0.25 $w t \%$, a slight increase of flow curve strain $\eta$ for low shear rates to 0.3 $s^{-1}$. For shear rates greater than 0.3 $s^{-1}$, the $\eta$ starts to decrease, as the polymer entanglements start to break apart, reducing friction between the polymer threads and therefore the viscosity also is reduced. The solution samples show a Newtonian-like behaviour and that may be caused by the use of the solvent cyclopentanone and by the small sized SU-8 2002 molecules.

@@

The flow curve results of Serie C are presented in Figure \ref{fig:SerieCflowCurve}. The sample with 1 $w t \%$ TBATFB concentration shows a shear thinning behaviour for shear rates varying between 0.1 to 15 $s^{-1}$. The 1 $w t \%$ sample describes a drop in viscosity for shear rates between 15 to 20 $s^{-1}$ followed by a stable state.

@@

\subsection{Rheological Characterization : \textbf{Frequency Sweep}}

@@

>>>>

\subsection{Rheological Characterization : \textbf{Flow Curve}}
Figure \ref{fig:SerieAflowCurve} shows evidence that the equal increase of PEO and TBATFB concentrations result in an increase of shear viscosity rate $\gamma$. for concentrations from 1.00 to 0.25 $w t \%$, a slight increase of flow curve strain $\eta$ for low shear rates to 0.3 $s^{-1}$. For shear rates greater than 0.3 $s^{-1}$, the $\eta$ starts to decrease, as the polymer entanglements start to break apart, reducing friction between the polymer threads and therefore the viscosity also is reduced. The solution samples show a Newtonian-like behaviour and that may be caused by the use of the solvent cyclopentanone and by the small sized SU-8 2002 molecules.

@@

The flow curve results of Serie C are presented in Figure \ref{fig:SerieCflowCurve}. The sample with 1 $w t \%$ TBATFB concentration shows a shear thinning behaviour for shear rates varying between 0.1 to 15 $s^{-1}$. The 1 $w t \%$ sample describes a drop in viscosity for shear rates between 15 to 20 $s^{-1}$ followed by a stable state. A similar behaviour is observed for concentration of 0.75 $w t \%$. and less evident for 0.0 $w t \%$. For concentrations of 0.5 $w t \%$ and 0.25 $w t \%$ the behaviour of the shear viscosity is similar.

@@

\subsection{Rheological Characterization : \textbf{Frequency Sweep}}
Figure \ref{fig:SerieAfreqSweep} shows that the solution with the lowest concentration of PEO and TBATFB has a decreasing behaviour of the viscosity, but for values greater to 3 $s^{-1}$ in frequency, the viscosity starts to increase. The solutions from 0.25 $w t \%$ to 1.00 $w t \%$ have the same shear-thinning behaviour. A direct relation between the concentrations and the viscosity values is discovered, where a small drop of viscosity is presented with the decrease of additive concentration.

\begin{figure}[th]
\centering
\includegraphics[width=0.75\textwidth]{./Figures/SerieAfreqSweep.png}
\decoRule
\caption[Serie A - Frequency Sweep]{Serie A - Frequency Sweep}
\label{fig:SerieAfreqSweep}
\end{figure}

Figure \ref{fig:SerieBfreqSweep} shows the frequency sweep results from Serie B. The presented behaviour is similar to Serie A. for the lower concentrations of PEO, the equipment has not enough sensibility to make measurements of the storage modulus because this one is very low. At PEO 0.25 $w t \%$, the viscosity remains almost constant at 1 $Pa s$, but as in Serie A a little variation of viscosity is presented at the lowest values of angular frequency. On the other hand, for the 0.5, 0.75 and 1.00 $w t \%$ concentrations, the viscosity is similar. At 100 $s^{-1}$, the three high concentration samples converge to 2 $Pa s$. It is imperative to assume that 0.5 $w t \%$ is the critical concentration, under this concentration the systems presents different behaviours since the molecules have enough room to diffuse and break entanglements. When the critical entanglement concentration is exceeded, the polymer threads overlap and become tangled, therefore no more entanglements are no longer possible.

\begin{figure}[th]
\centering
\includegraphics[width=0.75\textwidth]{./Figures/SerieBfreqSweep.png}
\decoRule
\caption[Serie B - Frequency Sweep]{Serie B - Frequency Sweep}
\label{fig:SerieBfreqSweep}
\end{figure}

The frequency sweep behaviours of Serie C are presented in Figure \ref{fig:SerieCfreqSweep}. The figure does not indicate a clear correlation between the viscosity and the addition of TBATFB. All samples have a similar behaviour and magnitude, except for the 0.75 $w t \%$ TBATFB concentration sample as it presents a non uniform behaviour. At low frequencies, the viscosity increases, then it remains constant at 20 $Pa s$ until a frequency value of 4 $s^{-1}$; the viscosity drastically decreases to 1 $Pa s$ and remains constant at that value. The 1.00 $w t \%$ sample has a decreasing viscosity behaviour at higher angular frequencies.

\begin{figure}[th]
\centering
\includegraphics[width=0.75\textwidth]{./Figures/SerieCfreqSweep.png}
\decoRule
\caption[Serie C - Frequency Sweep]{Serie C - Frequency Sweep}
\label{fig:SerieCfreqSweep}
\end{figure}

Flores work \cite{Flores2017} carried out a series of experiments in order to correlate the rheological properties of polymer solutions used in electro-mechanical spinning processes for the fabrication of carbon micro structures. Shear flow and dynamic measurements tests such as flow curves, amplitude sweeps and frequency sweeps were carried in an oscillatory rheometer to study the rheological behaviour of polymeric solutions of SU-8 2002, an epoxy-based negative photoresist, Poly(ethylene) oxide (PEO), a flexible, non-ionic polymer, and TBATFB (Tetrabutylammonium tetrafluoroborate) that acts as an electrolyte.

The concentrations of additives were varied from 0 $w t \%$ to 1.0 $w t \%$ with increments of 0.25. To observe the effects of each additive it was proposed a set of concentrations where both additives were equally varied (Serie A), TBATFB was constant the only PEO variations (Serie B), and PEO constant concentration with TBATFB variations (Serie C). It was found that the variation of the additives (PEO and TBATFB) affects the
rheological behavior of the solution. Typically, the addition of PEO increase the
elongational and shear viscosities while the addition of TBATFB modifies this property
but in a non-predictable manner. The solutions do not present yield stress as can be
seen in Amplitude Sweep and Frequency Sweep measurements.

@@

As stated by Cardenas \cite{Cardenas2017}, the following parameters play an important role in the graphitic content on the fabrication of carbon nano-wires through electrospinning:

\begin{enumerate}
\item The thickness of the produced polymeric wires,
\item the chemical composition and viscoelasticity of the polymeric solution,
\item the molecular alignment of the polymer,
\item the heat treatment temperature,
\item the mechanical pulling on the polymer jet during electrospinning,
\item the alifnment of polymer chains induced by the presence of an electric field, and
\item the catalysts and solvents within the polymer solution.
\end{enumerate}

Cardenas reviewed different polymer fabrication techniques and materials to produce carbon nano-wires. Within Cardenas' work the following parameters were evaluated to study the desirable characteristics for building highly sensitive sensor devices: a) the chemical composition and viscoelasticity of the polymer solution, b) the thickness of the produced polymeric wires, c) the mechanical pulling on the polymeric jet during electrospinning, and d) the alignment of the polymer chains induced by the presence of an electric field. Cardenas' work states that various methods are implemented to produce nanofibers, such as laser ablation, chemical vapor deposition, discharge, and vapour growth. However, those techniques are abandoned due to their low yield output and expensive equipment. Whereas electrospinning (ES) of polymer solutions is a promising technique for simple and inexpensive fabrication of carbon nano-wires, which can be combined with a moving collector to yield even thinner fibers.

The production of carbon sstructures involves to main procedures: a) polymer patterning such as photolithography, electrospinning, Computer Numerical Control (CNC), moulding, hot embossing, and recently, Multiple Photon Polymerization; and b) carbonization, which induces further thinning of the patterned polymer and its conversion into carbon. Cardenas conducted some experiments to characterize and analyse carbon nano-wires. Polymeric SU-8 nano fibers were produced by two different methods; for each method different polymer solutions were employed.

\subsection{Method 1 : }

\subsubsection{Polymer Solution}
The polymeric solution was composed by 2 $ml$ of SU-8 2002 mixed with 0.5 $w t \%$ of PEO and 0.5 $w t \%$ of TBATFB to increase its conductivity and yield soother polymer jets during electrospinning. Magnetic stirring was performed for 1 $hr$ at 75 \textdegree{}$C$ with $rpm$ values between 100 and 150.

\subsubsection{Deposition}
A voltage around 100 $V$ was applied between a dispensing needle and the collector stage. The needle to collector distance was set to 100 $\mu m$. The collector was attached to a mechanically motorized stage, which allowed the SU-8 nanofibers patterning into the SU-8 microstructures. Three different stage velocities were tested (20,40 and 60 $mm/s$) to study the influence on the wire geometry. Acceleration of the stage was set to 500 $mm/s^{2}$. After deposition, samples were exposed to UV light for 45 $min$ to complete cross-linking.

\subsection{Method 2 : }

\subsubsection{Polymer Solution}
The solution was composed of 4 $ml$ of SU-8 2025, 4 $mg$ of TBATFB and 80 $\mu L$ of SU-8 thinner. The solution was stirred for 1.5 $hrs$ at 100 $rpm$ at 75 \textdegree{}$C$.

\subsubsection{Deposition}
To pattern the fiber exactly on top of the SU-8 electrodes, a routine was set to move the needle relative to the collector. The polymer solution was dispensed at a rate of 8.847 $nL / min$ using a programmable syringe pump. A voltage of 200 $V$ was applied between the collector plate and the needle tip, and the polymer solution was allowed to flow for between 15 to 30 $min$ until it was stable. A higher voltage had to be applied compared to Method 1 due to the higher viscosity of the SU-8 2025 solution. Once a steady flow was achieved, the collector was moved relative to the needle tip using the motorized stage. The mechanical parameters used during were: a) velocity of 5000 $\mu m/s$, an acceleration of 2500 $\mu m/s^{2}$. The sample was exposed to UV light for 45 min to ensure complete cross-linking of the deposited SU-8 nanofiber.

\subsection{Results and Discussion}
To test the possibility of using SU-8 to fabricate carbon nano-wires, samples were pyrolyzed in an inert environment. Samples prepared by Method 1 failed the pyrolyzation as the deposited wires were mostly liquid before carbonization. The fibers produced by Method 2 had a yeild rate of 81 $\%$. The diameters after pyrolysis were analyzed and measured using SEM micrographs.

Cardenas \cite{Cardenas2017} states that the geometry of the carbon nano-wires is also an important characteristic that affects the carbon structure conductivity, mechanical and thermal characteristics and crystallinity. The conducted experiments showed some techniques and materials that have been applied to fabricate carbon nano-wires, as well as the effects that fabrication parameters have on the final geometry of the carbon structures. The newly technique of electro-mechano-spinning (EMS) involved new polymer solutions along with a systematic deposition process. Cardenas found that the EMS proposed manufacturing technique yielded normally distributed diameters of 204 $nm$ with low variability, which is significantly reduced the uncertainty in the fabrication of carbon nano-wires.
